What if you drop that? Modeling children's curiosity about physical interactions

### 2020-01-26 paper/paper.Rmd
para 3

The goal of the current paper is to help close this gap by proposin a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a lerner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by our computational theory and those taken by children on the same set of tasks.

@@

<!-- The places where curiosity is most manifest tend to be those open-ended environments that are hardest to model--an inviting playground or a surprisingly complex device. -->
<!-- Curiosity-driven behavior comes in a variety of contexts and consists of a wide repertoire of actions.  -->

<!-- While open-ended environments tend to inspire curiosity, choosing an appropriate paradigm, one in which learners both become curious and are able to choose a variety of actions to explore -->

Second, we need finer-grained measures of curiosity-driven behaviors.
What actions do learners select in order to gain information about the properties of objects and laws that govern the physical world? 
Past studies of infant's physical reasoning ability have used looking time to measure their knowledge about physical events, given that infant's attend longer to surprising events [e.g., objects appearing to pass through a wall; @Stahl2015].
Behavioral investigations of older children's exploratory play have also used simple attention duration measures to measure curiosity, for example offering children a single complex toy with a number of functions that can be discovered [e.g., @Cook2011; @Bonawitz2012; @Gweon2014], and tallying the number of discovered functions.
However, these attention and discovery measures do not quantify the overt actions that children choose, and typically do not offer more than one or two target objects for exploration. 
Further, most environments that inspire curiosity tend to be more open-ended and afford a much wider variety of action choices.

A third desiderata for a testable theory of curiosity is a linking function for evaluating the correspondence between the predictions of our computational theory and the observed patterns of action selection that infants and children show in the same physical task. 
Although behavioral studies of young children have found that they preferentially play with toys in order to learn the causal structure [@Schulz2007; @Gweon2014], there has been no detailed formal account of what their play actions are, or how they are selected in a given situation.
Infant studies of surprisal to various physical events involving occlusion, containment, and covering of objects has revealed that even very young infants are unsurprised by many physical interactions [see @Baillargeon2007], but these studies do not specify or predict what physical interventions infants may make in order to learn more about the properties of objects and the laws of physics.

>>>>

The goal of the current paper is to help close this gap by proposing a framework for advancing our theoretical understanding of curiosity that combines three key ingredients: _first_, we present a computational theory of how a lerner's knowledge state interacts with ongoing perceptual experiences to give rise to curiosity-driven exploratory behavior; _second_, we present an empirical investigation of the pattern of actions taken by children in a novel physical exploration task; and _third_, we evaluate the quantitative correspondence between the exploratory actions taken by an artificial agent that instantiates our computational theory and those taken by human children on the same set of tasks.

@@

<!-- The places where curiosity is most manifest tend to be those open-ended environments that are hardest to model--an inviting playground or a surprisingly complex device. -->
<!-- Curiosity-driven behavior comes in a variety of contexts and consists of a wide repertoire of actions.  -->
<!-- While open-ended environments tend to inspire curiosity, choosing an appropriate paradigm, one in which learners both become curious and are able to choose a variety of actions to explore -->
<!-- Second, we need finer-grained measures of curiosity-driven behaviors. -->
<!-- What actions do learners select in order to gain information about the properties of objects and laws that govern the physical world?  -->

Our empirical study is motivated by a large body of prior work in developmental psychology investigating the development of knowledge about physical objects, their properties, and how they interact (CITECITECITE), thus making exploration of physical objects a natural choice of domain to explore the implications of our theory. However, the measures used in this literature have typically been coarse-grained with respect to infant's and children's physical knowledge. For instance, a typical measure of physical curiosity has been longer looking times to surprising events than to expected events (e.g., objects appearing to pass through a wall; @Stahl2015). Other work that has investigated exploratory behavior in children have used more granular measures, such as counting the number of functions discovered while playing with novel and complex toy [e.g., @Cook2011; @Bonawitz2012; @Gweon2014] However, what both of these looking-time and toy-exploration measures fail to capture are the ways in which children actively learn by intervening on the world and observing the consequences of their actions [@Gopnik2009, @gureckis2012self]. To address this limitation, we developed a novel physical exploration task in which children choose which series of physical experiments to perform and observe the results of each in real time.

Our strategy for evaluating the correspondence betweenour computational theory and the observed patterns of action selection is to  children show in the same physical task. 
Although behavioral studies of young children have found that they preferentially play with toys in order to learn the causal structure [@Schulz2007; @Gweon2014], there has been no detailed formal account of what their play actions are, or how they are selected in a given situation.
Infant studies of surprisal to various physical events involving occlusion, containment, and covering of objects has revealed that even very young infants are unsurprised by many physical interactions [see @Baillargeon2007], but these studies do not specify or predict what physical interventions infants may make in order to learn more about the properties of objects and the laws of physics.
